

```{r}

#install.packages("HistData",  repos = "http://cran.us.r-project.org", dependencies=TRUE) 
library("HistData")
data(GaltonFamilies)
Galton2 <- data.frame(GaltonFamilies)
names(Galton2)

```

1. Obtain the summary of the data GaltonFamilies


```{r}
summary(Galton2)

```


2. Are there any data that should be coded missing?


```{r}
#install.packages("mice", repos = 'http://cran.rstudio.com')

library(mice)
M=md.pattern(Galton2)
M

```

Ans- No, we don't see any variables which shows missing data



3. Which variables are numeric, integer, or factor?

```{r}
str(Galton2)

```

Ans- Numeric Variables- 'father', 'mother', 'midparentHeight', 'childHeight'
Interger Variables- 'children', 'childNum'
Factor- 'family', 'gender'



4. What is the R command for obtaining the levels of a factor?

Ans-  R command for obtaining levels of a factor are - levels(dataname)


5. Use this command to determine the levels of gender

```{r}
levels(Galton2$gender)

```

6. Are the labels sufficiently informational?

```{r}
 str(Galton2$gender)
```


Ans- The lables of 'Levels' has reference level set at 'female' meaning female having lower value and male having higher value. This is not the general trend followed now. Also, 
from above str command we can infer that Female has been assigned numeric value '1' and male value of'2' which is not consistent with the 'Gender' variable generally defined.

Thus the lables are not sufficiently informational.



7. Remove the family and childNum columns


```{r}

dt<-subset(Galton2, select=-c(family,childNum))

```



8. Produce the summary table of the modified dataframe


```{r}
summary(dt)

```


    
    






